Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-26 PAPER.tex
added some more refs

By about one billion years after the Big Bang ($z \sim 6$), the first stars and galaxies are thought to have ionized all the 
neutral hydrogen that dominated the baryonic matter content in the Universe. This transition period, during which the first 
luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas 
into a plasma, is known as the Epoch of Reionization (EoR). The EoR is a relatively unexplored era in our \textit{cosmic dawn}, which spans from the birth of the first stars to the full reionization of the intergalactic medium (IGM). Its 
history encodes important information regarding the nature of the first galaxies and the processes of structure formation. 
Direct measurements of the EoR would unlock powerful characteristics about the IGM, revealing connections 
between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
web of galaxies we observe today (for a review, see \citet{furlanetto_et_al2006} and \citet{loeb_furlanetto_2013}).

One promising technique to probe the EoR is to target the 21\,cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}). This tomography technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength 
of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
stretching out as it traveled through expanding space. Tracing the 21\,cm line as a function of redshift offers a window into the 
evolution of ionization, temperature, and density fluctuations.

@@

The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}. A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, errors, and bias) that are essential to investigate 
for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 power spectrum 
from the lessons learned.

@@

The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with foreground cleaning of GBT data. Therefore, in our revised 
signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
weighted power spectrum of the data from the weighted power spectrum of data plus EoR.

>>>>

By about one billion years after the Big Bang ($z \sim 6$), the first stars and galaxies are thought to have ionized all the 
neutral hydrogen that dominated the baryonic matter content in the Universe. This transition period, during which the first 
luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas 
into a plasma, is known as the Epoch of Reionization (EoR). The EoR is a relatively unexplored era in our \textit{cosmic dawn}, which spans from the birth of the first stars to the full reionization of the intergalactic medium (IGM). Its 
history encodes important information regarding the nature of the first galaxies and the processes of structure formation. 
Direct measurements of the EoR would unlock powerful characteristics about the IGM, revealing connections 
between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
web of galaxies we observe today (for a review, see \citet{barkana_and_loeb2001}, \citet{furlanetto_et_al2006} and \citet{loeb_furlanetto_2013}).

One promising technique to probe the EoR is to target the 21\,cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{barkana_and_loeb2008}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_and_loeb2010}; \citealt{pritchard_loeb2012}). This tomography technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength 
of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
stretching out as it traveled through expanding space. Tracing the 21\,cm line as a function of redshift offers a window into the 
evolution of ionization, temperature, and density fluctuations.

@@

The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}. A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, errors, and bias) that are essential to investigate 
for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 power spectrum 
from the lessons learned.

@@

The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with foreground cleaning of Great Bank Telescope (GBT) data. Therefore, in our revised 
signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
